---
title: "Datasets"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MATH3823 Datasets

::: callout-important
You are reminded of the information in the Lecture Notes:

Unless otherwise stated, data files will be available online at: richardpmann.com/MATH3823/Datasets/*filename.ext*, where *filename.ext* is the stated filename with extension.
:::

In Exercise 1.1, you can access the file here: [beetle.txt](https://richardpmann.com/MATH3823/Datasets/beetle.txt) but also it can be read-in directly from within R using:

```{r}
beetle = read.table("https://richardpmann.com/MATH3823/Datasets/beetle.txt", header=T)
```

In Exercise 1.5, you can access the file here: [physics_from_data.csv](https://richardpmann.com/MATH3823/Datasets/physics_from_data.csv) but also it can be read-in directly from within R using: 

```{r}
physics = read.csv("https://richardpmann.com/MATH3823/Datasets/physics_from_data.csv", header=T)
```

In Exercise 2.4, you can access the file here: [barley.csv](https://richardpmann.com/MATH3823/Datasets/barley.csv) but also it can be read-in directly from within R using: 

```{r}
barley = read.csv("https://richardpmann.com/MATH3823/Datasets/barley.csv", header=T)
```


::: callout-important
Please note that this level of guidance will not be given routinely and hence please follow the equivalent approach using the general folder address and specific file name. 
:::